The journey of Multiple Sequence Alignment

### 2021-07-28 MSA_Notum_journey.Rmd
add iqtree and iqtree results with MUSCLE msa

# print an example of the results 
```{r eval = TRUE}
notum_blst %>% arrange(evalue)
```

# get the 10 top hits identifiers
```{r eval = TRUE}
top10_seqs <- notum_blst %>% arrange(evalue) %>% head(11) %>% .$subject_id
```

# import fasta db
import the sequences and filter them for the 10 best hits from the previous results in order to make the multiple sequence alignments
```{r eval = TRUE}
suppressPackageStartupMessages({
library(Biostrings)
  })
fasta_db <- readAAStringSet("oma_db")

@@

# print the MSA
```{r eval = TRUE}
print(myFirstAlignment, show="complete")
```

# get significant sequences
```{r eval = TRUE}
sign_seqs <- notum_blst %>% filter(evalue < 0.05) %>% .$subject_id

@@

# perform MSA with MUSCLE
```{r}
sign_seqs_muscle <- msaMuscle(fasta_db_fil)
sign_seqs_bio2mds <- msa::msaConvert(sign_seqs_muscle, type = "bios2mds::align")
export.fasta(sign_seqs_bio2mds, outfile = "sign_seqs_msa_muscle.fa", ncol = 60, open = "w")
```
check the sign_seqs_msa_muscle.fa file for the alignments

>>>>

## print an example of the results 
```{r eval = TRUE}
notum_blst %>% arrange(evalue)
```

## get the 10 top hits identifiers
```{r eval = TRUE}
top10_seqs <- notum_blst %>% arrange(evalue) %>% head(11) %>% .$subject_id
```

## import fasta file with all sequences
import the sequences and filter them for the 10 best hits from the previous results in order to make the multiple sequence alignments
```{r eval = TRUE}
suppressPackageStartupMessages({
library(Biostrings)
  })
fasta_db <- readAAStringSet("oma_db")

@@

## print the MSA
```{r eval = TRUE}
print(myFirstAlignment, show="complete")
```

## get significant sequences
```{r eval = TRUE}
sign_seqs <- notum_blst %>% filter(evalue < 0.05) %>% .$subject_id

@@

## perform MSA with MUSCLE
```{r}
sign_seqs_muscle <- msaMuscle(fasta_db_fil)
sign_seqs_bio2mds <- msa::msaConvert(sign_seqs_muscle, type = "bios2mds::align")
export.fasta(sign_seqs_bio2mds, outfile = "sign_seqs_msa_muscle.fa", ncol = 60, open = "w")
```
check the sign_seqs_msa_muscle.fa file for the alignments

# IQTREE
```{bash}
docker run --rm -ti -v $(pwd):/home/my_data staphb/iqtree

cd home
mkdir my_data/my_first_tree

iqtree -s my_data/sign_seqs_msa_muscle.fa -nt 6 -mset LG -pre my_data/my_first_tree/my_tree

```
